### 2021-11-25 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@e3eace70cbd0949351a6bc37146e430c2115ef4b 🚀

Building models for ecological forecasting is an imperative (Dietze
\emph{et al.} 2018), but before applying forecasting methods to actual
data, we need a way to determine the efficacy of different forecasting
methods. We need a software library like this to generate synthetic data
from a \emph{known} set of mechanisms and parameters to test our methods
for parameter inference and forecasting on a system with \emph{known}
ground-truth dynamics to assess the effectiveness of these inference and
forecasting methods.

>>>>

Building models for ecological forecasting is an imperative (Dietze
\emph{et al.} 2018), but before applying forecasting methods to actual
data, we need a way to determine the efficacy of different forecasting
methods. We need a software library to generate synthetic data from a
\emph{known} set of mechanisms and parameters to test our methods for
parameter inference and forecasting on a system with \emph{known}
ground-truth dynamics to assess the effectiveness of these inference and
forecasting methods.
